\documentclass[Report.tex]{subfiles}
\begin{document}
	
	When moving into interactive visualization, going web--based is a very reasonable choice. When working with the programming interface of web-pages, the Document Object Model (\emph{DOM}), the standard is to use a few different languages. To define the content of a page, Hyper Text Markup Language (\emph{HTML}) is used. \emph{HTML} by itself does not provide many options regarding styling, this is where Cascading Style Sheets (\emph{CSS}) comes in. Using \emph{CSS}, \emph{DOM} elements can be styled to ones desire. However, even then, there is still two quite important components for effective visualization missing. Firstly, \emph{HTML} is mostly made for handling text and images, not generating shapes. This is where Scalable Vector Graphics (\emph{SVG}) comes along. \emph{SVG} has some relatively simple shapes built in, such as rectangles and circles, as well as the powerful \texttt{path} tag. Using this tag, very sophisticated shapes can be made. Being a vector graphics format, means that \emph{SVG}, will have sharp edges, and generally look as intended no matter how far it is scaled.\\
	Even with all that, there is still no interactivity. This is where \emph{JavaScript} comes along. Being a scripting language for the \emph{DOM}, \emph{JavaScript} is a very powerful tool to have, as it provides runtime modification of the \emph{DOM}. \\\emph{JavaScript} has the ability to listen for events on \emph{DOM} elements, such as mouse clicks, which is what allows dynamically changing visualizations based on user interaction.\\
	Now, just because we have these languages available, does not mean that creating visualizations will be child's play. With plain \emph{JavaScript}, going from data to interactive visualizations would be quite a journey.
	\\
	This is where the \emph{JavaScript} Library Data-Driven Documents (\emph{D3}) turns out to be a powerful and versatile choice.\\ 
	Before \emph{D3}, the people behind it worked on a visualization framework under the name "Protovis" \cite{Protovis}. Built with the focus of a user being able to pump out visualizations without much effort, the framework wasn't built for letting the user work directly with the standards mentioned earlier. This lead to slow adoption of the framework, and inefficient use. These, among other things is described more in-depth in the article "D3: Data-Driven Documents"\cite{D3}.\\
	
	The resulting \emph{D3} provides powerful tools for binding data to the \emph{DOM}, while leaving the creation of visualizations to the user of the library. This way the user can utilize the synergy between \emph{HTML}, \emph{SVG}, \emph{CSS} and \emph{JavaScript}.
	
	%Delete?
	\paragraph{Delete?\\}
	\emph{D3} is designed to work on most "modern" internet browsers, \textit{which generally means everything except IE8 and older versions.} \cite[Browser / Platform Support]{D3W}\\
	 This is done through creating a selection, on which the \texttt{.data()} function is called. This function joins the selection with the array provided as parameter, returning a new selection. On this selection the \texttt{.enter()} and \texttt{.exit()} selection functions can be called, \texttt{.enter()} returning a selection placeholder nodes for the data that had no DOM elements in the selection, and \texttt{.exit()}, the selection of existing DOM elements, which had no data points in the selection. DOM elements can then be added or removed based on these selections.\\
	Although D3 can be used to create HTML tables etc. the most common use of D3 for visualization purposes, is through Scalable Vector Graphics (SVG).
	SVG is based on XML, and can be modified / styled on the go through JavaScript for editing the SVG elements, and CSS for styling them. The CSS styling can be set and/or modified at runtime through JavaScript as well. Because of this, the programmer have the possibility to create visualizations that react to what the user is doing in interesting ways, or create dynamic visualizations.\\
	Another reason to use SVG over raster image formats, is that it will look as intended no matter how far it is scaled, where raster images like png or jpeg become pixelated when scaled.
	One of the core features in d3 is the Scales sub-library, which provides functionality that can transform all data given to fit inside the given range, while still maintaining the relative position / size between elements.
	This is especially useful when designing responsive web pages, where dimensions of the SVG element may differ.\\
	D3's SVG sub-library brings generators for several non-standard shapes in SVG. These generators can generate SVG paths which resemble the shapes. Some of these shapes are lines, arcs and chords. These shapes can be modified with options such as interpolation, which can be used to smoothen lines in a line chart, while they are still styleable through CSS.\\
	
	While this way of doing visualizations is preferred in a lot of cases due to reusability, and user interactivity, working with large datasets can give unwanted results. 
	If the user has to load more than a few megabytes of data in order to create the visualization, it is going to take some time, and if that data result in a large amount of SVG elements, a dynamic or interactive visualization could become unresponsive, which is undesired, as it will lower user experience.
\end{document}

