\documentclass[Report.tex]{subfiles}
\begin{document}
\section*{Process Evaluation}
\pagestyle{empty}
At our first meeting in the group we made the group contract. We discussed how we would like to distribute our work and what we should do to cooperate in the most successful way. Early in our process we also met with the company Prozone, which is the company providing us with data. Here we got information about their data, current tools, what they could be interested in and what they could offer us. It seemed very promising but unfortunately the process of getting the data was a longer than expected. It took around a month to get access to the API, which of course was a challenge, because we did not know exactly what data we could get access to. We got some data from the beginning, but this was of very scarce quantity. Because of that most of our visualizations are based on this test data, and scaled up when we finally got access to more.

Because of the lack of data, we focused on the theory the first few weeks. We explored  theoretical materials on our own, and later on discussed them in the group. This has generally been the process of our work. Also when getting access to the API we could start to share knowledge about the data we could get. We have programmed our visualizations individually and helped each other to understand the programming languages. If one had problems we tried to solve these together. During the design process we also gave each other feedback on the specific visualizations. 

At the midway seminar we had some ideas about what we would like to visualise, and had some basic visualizations to show. There was a general structural feedback on our presentations, like missing slide numbers, slide titles and conclusion slide. We needed a greater theoretical knowledge too, making us able to answer any questions, and explain every topic we mention. Lastly our supervisor emphasised the importance of using original and innovative graphics, which not all members did.

At one of our meetings we talked about which theoretical topics we would like to include in our report. Afterwards we delegated the different sections between us.  In the end we read each others sections to check for spelling mistakes, typos but more importantly to agree on the content. Each member has written their own results section, and contributed to the discussion and conclusion section from this. We agreed on when to  finish with the theory sections, but this deadline was not met by most of the group members. This meant that the last week has been somewhat stressful for some group members.

Generally the group has met a couple of times a week, to discuss progress and theory. We evaluated how long we had come, and what the next step was. We met once a week with our supervisor to get feedback on our work. The group meetings have typically been placed before and after each meeting with our supervisor, to discuss what our agenda to the supervisor meeting would be, and what we should do next based on the feedback from our supervisor. At almost every group meeting every member was present, and most of the time arriving on time. We have generally given members who was late a few minutes before we started the meeting. After each meeting we have posted entries to the journal concerning what we have accomplished, and what we would do next.

We have been using Github to share all our materials. We have uploaded most of the sources, together with all our visualizations and documents. It has made the work much easier because we could get updates on each others work and get inspired just by looking at the uploaded materials. Also when writing the report it has been very helpful, especially combined with a \LaTeX \space document for each section, meaning that each member could write in their own document, and just link it to the final document.

We have had no major conflicts, only minor disagreements with our supervisor about what we thought the project should be about, and which topics we should include. Our supervisor suggested to include some machine learning, which we thought was a bit off topic. In the end we decided not to include it. The group has worked together in mutual respect for each other, no conflicts have risen.

From slides on e-learn we got a time line over the project but have had big problems following this, because of the late data arrival. A lot of time has also been wasted on email correspondence with Prozone concerning the data. This also means that the process has been somewhat even more compressed and pushed to the end. 

Concerning the mandatory \LaTeX\space and library courses we have the following comments. The library course was informative, and gave us some knowledge of where to find materials and what to use. We already had plenty of materials, so we have not used the knowledge much. The \LaTeX \space courses were not so informative, because we were already used to writing in \LaTeX, only few informations were valuable for us. The course about poster creation in \LaTeX\space was not useful at all. A few examples was explained, and we could begin to make our posters, and the instructor could help us. The structure would be great if the course had been later in the process, we did not begin creation of the poster because we were not ready for it.

When having to evaluate the process it is our opinion that we should have been working even more together in the same room, discussing our temporary results and discoveries. In the last couple of weeks we worked more intensively together, which yielded great results, and which showed new opportunities which we could have followed if we had the time. It worked out nicely to study the theory individually and then talk about it, if we had any doubts, but once again it could have been a great idea, maybe to study different parts of theory and then explain it to the others. In this way we could have covered a larger field without having to individually read it all by our self. This would also be a great way to practise explaining the theory for others. In relation to the deadlines not being respected, we should have been more honest with each other, and talked about why this was the case. Earlier in the project, we should have made deadlines for bringing concrete visualizations, such that we would be more on the same level in the process and could have improved our visualizations even further.
\thispagestyle{empty}


\end{document}