%Name of section: "Football data"

\documentclass[Report.tex]{subfiles}

\begin{document}

The data that we use in our visualizations come from two different places. The first place is from an Excel sheet with data about the football teams in the ``Superliga'' (now referred to as the \emph{league}), which we were sent by Prozone (the company that is giving us access to their football data). That data is already somewhat processed and it is convenient to work with it in R, as one doesn't have to do any API calls. The second place that we get our data from is through an API that Prozone has given us access to. The API works in this way: one goes to their website and browses the different things one can request. When one has found what one needs, one receives a URL where one can append arguments, for example specify a team id or the encoding format (XML or JSON). When that is done, one needs to generate a signature, which is the current unix time plus a shared key and an API key, which we have been provided by Prozone. That string is then hashed using SHA-256, and appended onto the request URL along with the shared key unhashed. Then one simply sends a HTTP GET-request, and one receives the data in the response. The request link is only valid for a short period of time, meaning that generally, if anything interesting has to be done, the requests have to be generated automatically. For this purpose, a function has been implemented in R, which automatically generates the request URL and returns a data frame, when given the first part of the URL, which describes what data is desired. The function is especially useful when one has to retrieve large amounts of data from the API, as some of the data can be very tedious to get from the API. 

The data that we have access to through the API is things such as a list of all football teams in the league, their rankings and so on as well as data from specific matches. An example of what one has to do to get all of the goal attempts throughout the season is: First get a list of all football teams in the league. For each football team get a list of the matches that they have participated in. For each match retrieve the events in that match, and put all of those events into one big data frame, and then filter the events such that only goal attempts are left. What is important to note about the API is that one cannot simply say for example ``return all matches where there are at least 5 goal attempts within 10 minutes''. One has to make a program which makes multiple calls to the API and based on the responses, decides what other calls should be made.

%someone can add more here if they wish to.. this was the first things that popped into my mind
A short list of some of the data we can get through the API is the following:
\begin{itemize}
\item Football teams in the league
\item Statistics about a football team (goal attempts, points, number of players, city of origin etc.)
\item Players on a team
\item Information about a player (height, weight, age etc.)
\item Matches a team has participated in
\item Statistics about a match (outcome, injuries, event data etc.)
\end{itemize}

\end{document}